### 2021-02-22 architecture.tex
Clarify why we omit problem in notation of c

The symbol cost of each symbol is computed by passing the symbol's embedding through a dense layer with a single output unit.
No activation function is applied so that the output values can span the whole $\re$.
\todo{MS: provided the input embeddings can...}

Note that it is possible to use a more complex projection module,
e.g., a feed-forward network with one or more hidden layers.
\todo{FB: Ensure the term is defined.}
Our experiments showed no significant improvement when a hidden layer was added,
likely because the underlying \gls{gcn} learns a sufficiently complex transformation.

For input problem $P$
with signature $\Sigma = (s_1, \ldots, s_n)$,
we denote the cost of the $i$-th symbol as $c(i)$.
\todo{FB: Consider using $c(s_i)$.}
\todo{FB: Consider making the background problem explicit by using $c(i|P)$ or $C(i,P)$.}

>>>>

The symbol cost of each symbol is computed by passing the symbol's embedding through a fully-connected layer
with a single output unit.
No activation function is applied on the output values.
\todo{FB: Explain why.}

It is possible to use a more complex output layer,
e.g., a feedforward network with one or more hidden layers.
Our experiments showed no significant improvement when a hidden layer was added,
likely because the underlying \gls{gcn} learns a sufficiently complex transformation.

Let $\theta$ denote the vector of all the parameters of the \gls{gcn} and the output layer.
Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
we denote the cost of symbol $s_i$ as $c_{\theta,P}(i)$,
or simply $c(i)$ in case the parameters $\theta$ and the problem $P$ are fixed in the context.
